Embedding Intuitionistic into Classical Logic

### 2022-10-14 FoSSaCS/fossacs-EIICL.tex
Update fossacs-EIICL.tex

\begin{wrapfigure}[13]{r}{0.4\textwidth}
	\vspace*{4.9cm}
	\hspace*{1cm}
	\begin{tikzpicture}
		\begin{scope}[opacity=0.3, blend mode=multiply]
			\def\firstcircle{(90:.75) circle (1.5)}
			\def\secondcircle{(210:.75) circle (1.5)}
			\def\thirdcircle{(330:.75) circle (1.5)}
			\begin{tikzpicture}
				\begin{scope}[shift={(3cm,-5cm)}, fill opacity=0.5]
					\fill[red] \firstcircle;
					\fill[green] \secondcircle;
					\fill[blue] \thirdcircle;
					\draw node {$491$};
					\draw node at (30:1.2) {$30$};
					\draw node at (150:1.2) {$42$};
					\draw node at (270:1.2) {$22$};
					\draw node at (90:1.8) {$8$};
					\draw node at (210:1.8) {$2$};
					\draw node at (330:1.8) {$417$};
				\end{scope}
			\end{tikzpicture}
		\end{scope}
	\end{tikzpicture}
	\vspace*{-7.1cm}
	\caption{Symmetric difference. Instances proven by Embedding (red), Embedding (idem.) (green), ileanCoP or nanoCoP (blue)}
	\label{fig:c}
\end{wrapfigure}

@@

Two versions of the translation were tested, one with and one without the additional axioms encoding idempotence. The results are stated in Figure \ref{fig:a}. 
In general, our approach falls short of the state of the art. 
However when grouping the benchmarks by $|\mathcal Q|$ and $|\mathcal X|$, see Figure~\ref{fig:b},
we observe good performance of our approach for $|\mathcal Q| = 0$ and $|\mathcal X| \leq 2$ resp. $|\mathcal X| \geq 6$.
Figure~\ref{fig:c} shows that our approach solved 52 problems not solved by the state-of-the-art provers.\pagebreak
\begin{figure}
	\centering
	\begin{tabular}{c|c|lr|lr|lr|lr|c}
		$|\mathcal Q|$&$|\mathcal X|$&\multicolumn{2}{c}{Embedding}&\multicolumn{2}{c}{Embedding (idem.)}&\multicolumn{2}{c}{ileanCoP}&\multicolumn{2}{c}{nanoCoP-i 2.0}&Total\\\hline
		0&0		&157&88.2\%	&157&88.2\%		&128&71.9\%		&61&38.1\%	&178\\
		0&1-2	&119&29.8\%&130&32.5\%		&108&27.0\%		&96&24.0\%	&400\\
		0&3-5	&16&15.2\%	&17&16.2\%		&50&47.6\%		&40&28.1\%	&105\\
		0&6+	&27&38.6\%	&11&15.7\%		&20&28.6\%		&11&15.7\%	&70\\
		1-2&0-2	&84&29.3\%	&81&28.2\%		&227&79.1\%		&221&77.0\%	&287\\
		1-2&3-5	&80&25.6\%	&77&24.7\%		&141&45.2\%		&122&39.1\%	&312\\
		1-2&6+	&22&21.8\%	&21&20.8\%		&39&38.6\%		&37&36.6\%	&101\\
		3-5&0-5	&38&17.0\%	&40&17.9\%		&125&55.8\%		&110&49.1\%	&224\\
		3-5&6+  &20&8.4\%	&18&7.6\%		&64&27.0\%		&86&36.3\%	&237\\
		6+&0+	&8&1.1\%	&5&0.7\%		&73&9.7\%		&74&9.8\%	&755
	\end{tabular}
	\caption{Solved problems grouped by $|\mathcal Q|$ and $|\mathcal X|$.}
	\label{fig:b}
\end{figure}
\vspace*{-.5cm}

We conclude that our approach already has merits when $|\mathcal X|$ and $|\mathcal Q|$ are small. 
We see that encoding idempotence does help to solve some additional benchmarks, but in general does not improve performance.
However, idempotence is a quite powerful concept from a model-theoretic perspective. We suspect that a more clever encoding of this property could improve our results. There are other restrictions on models we could consider, based on structural properties of the formula, e.g. the relation between occurrences of different atoms.

>>>>

\begin{wrapfigure}[13]{r}{0.4\textwidth}
	\vspace*{4.9cm}
	\hspace*{1cm}
	\begin{tikzpicture}
		\begin{scope}[opacity=0.1, blend mode=multiply]
			\def\firstcircle{(90:.75) circle (1.5)}
			\def\secondcircle{(210:.75) circle (1.5)}
			\def\thirdcircle{(330:.75) circle (1.5)}
			\begin{tikzpicture}
				\begin{scope}[shift={(3cm,-5cm)}, fill opacity=0.5]
					\fill[red] \firstcircle;
					\fill[green] \secondcircle;
					\fill[blue] \thirdcircle;
					\draw node {$491$};
					\draw node at (30:1.2) {$30$};
					\draw node at (150:1.2) {$42$};
					\draw node at (270:1.2) {$22$};
					\draw node at (90:1.8) {$8$};
					\draw node at (210:1.8) {$2$};
					\draw node at (330:1.8) {$417$};
				\end{scope}
			\end{tikzpicture}
		\end{scope}
	\end{tikzpicture}
	\vspace*{-7.1cm}
	\caption{Instances proven by combinations of Embedding (red), Embedding (idem.) (green), ileanCoP or nanoCoP (blue)}
	\label{fig:c}
\end{wrapfigure}

@@

Two versions of the translation were tested, one with and one without the additional axioms encoding idempotence. The results are stated in Figure \ref{fig:a}. 
In general, our approach falls short of the state of the art. 
However when grouping the benchmarks by $|\mathcal Q|$ and $|\mathcal X|$, see Figure~\ref{fig:b},
we observe good performance of our approach for $|\mathcal Q| = 0$ and $|\mathcal X| \leq 2$ resp. $|\mathcal X| \geq 6$.
Figure~\ref{fig:c} shows that our approach solved 52 problems not solved by the state-of-the-art provers. Notably, while there is great overlap in solved instances, ileanCoP and nanoCoP also have a significant symmetric difference.\pagebreak
\begin{figure}
	\centering
	\begin{tabular}{c|c|lr|lr|lr|lr|c}
		$|\mathcal Q|$&$|\mathcal X|$&\multicolumn{2}{c}{Embedding}&\multicolumn{2}{c}{Embedding (idem.)}&\multicolumn{2}{c}{ileanCoP}&\multicolumn{2}{c}{nanoCoP-i 2.0}&Total\\\hline
		0&0		&157&88.2\%	&157&88.2\%		&128&71.9\%		&61&38.1\%	&178\\
		0&1-2	&119&29.8\%&130&32.5\%		&108&27.0\%		&96&24.0\%	&400\\
		0&3-5	&16&15.2\%	&17&16.2\%		&50&47.6\%		&40&28.1\%	&105\\
		0&6+	&27&38.6\%	&11&15.7\%		&20&28.6\%		&11&15.7\%	&70\\
		1-2&0-2	&84&29.3\%	&81&28.2\%		&227&79.1\%		&221&77.0\%	&287\\
		1-2&3-5	&80&25.6\%	&77&24.7\%		&141&45.2\%		&122&39.1\%	&312\\
		1-2&6+	&22&21.8\%	&21&20.8\%		&39&38.6\%		&37&36.6\%	&101\\
		3-5&0-5	&38&17.0\%	&40&17.9\%		&125&55.8\%		&110&49.1\%	&224\\
		3-5&6+  &20&8.4\%	&18&7.6\%		&64&27.0\%		&86&36.3\%	&237\\
		6+&0+	&8&1.1\%	&5&0.7\%		&73&9.7\%		&74&9.8\%	&755
	\end{tabular}
	\caption{Solved problems grouped by $|\mathcal Q|$ and $|\mathcal X|$.}
	\label{fig:b}
\end{figure}
\vspace*{-.5cm}

We conclude that our approach already has merits when $|\mathcal Q| = 0$ and $|\mathcal X|$ is small. 
We see that encoding idempotence does help to solve some additional benchmarks, but in general does not improve performance.
However, idempotence is a quite powerful concept from a model-theoretic perspective. We suspect that a more clever encoding of this property could improve our results. There are other restrictions on models we could consider, based on structural properties of the formula, e.g. the relation between occurrences of different atoms.
